Explore resilience evi

### 2017-11-24 analysis/evi/explore_resilience.Rmd
add anovas table

@@

  out <- list()  
  out$mest <- mest # Huber M-estimators and Confidence Intervals
  out$mest_a <- mest_a
  out$mest_b <- mest_b
  out$ra <- out_ra # Output for Two-way robust analysis (M-estimators)
  out$raTrimmed <- out_raTrimmed
  out$ph <- ph # posthoc comparison usinng pairwiseRobustTest 
  out$pha <- pha
  out$phb <- phb
  out$phab <- phab

@@

@@

write.csv(pairwise, file=paste0(di, '/out/anovas_resilience/huber_evi/robust_pairwise.csv'), row.names = F)
```

>>>>

  out_ratr_df <- data.frame(var = c(out_raTrimmed$varnames[2], 
                                    out_raTrimmed$varnames[3], 
                                    paste0(out_raTrimmed$varnames[2], ':', out_raTrimmed$varnames[3])),
              statistic = c(out_raTrimmed$Qa, out_raTrimmed$Qb, out_raTrimmed$Qab),
              pvalue = c(out_raTrimmed$A.p.value, out_raTrimmed$B.p.value, out_raTrimmed$AB.p.value))

@@

  out <- list()  
  out$mest <- mest # Huber M-estimators and Confidence Intervals
  out$mest_a <- mest_a
  out$mest_b <- mest_b
  out$ra <- out_ra # Output for Two-way robust analysis (M-estimators)
  out$raTrimmed <- out_raTrimmed
  out$out_ratr_df <- out_ratr_df
  out$ph <- ph # posthoc comparison usinng pairwiseRobustTest 
  out$pha <- pha
  out$phb <- phb
  out$phab <- phab

@@

```{r}

rars$out_ratr_df$var <- 'rs'
rarc$out_ratr_df$var <- 'rc'
rart$out_ratr_df$var <- 'rt'
rarrs$out_ratr_df$var <- 'rrs'

trimmedanovas <- rbind(rarc$out_ratr_df, rart$out_ratr_df, rars$out_ratr_df, rarrs$out_ratr_df) 
trimmedanovas %>% pander()

@@

write.csv(pairwise, file=paste0(di, '/out/anovas_resilience/huber_evi/robust_pairwise.csv'), row.names = F)
write.csv(trimmedanovas, file=paste0(di, '/out/anovas_resilience/huber_evi/trimmed_anovas.csv', row.names = F)
```
